---
name: Erin
surname: Robinson
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: 
position: "Digital Infrastructure Designer + Facilitator"
#profilepic: ErinHeadshot.png
#phone: 0996597844
email: erin@metadatagamechnagers.com
github: erinmr
linkedin: erinmr
orcid: 0000-0001-9998-0114
www: erinrobinson.info
header-includes:
  - \setstretch{1.15}
headcolor: 3b3bc4
output: 
  vitae::awesomecv
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(magrittr)
source("Utils/data_download_funs.R")

CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1Q_BUBgZ7wRJ6VWRw95shYGduhNDK9mLQaKfa65a3KW0/edit?usp=sharing",  
  pdf_mode = FALSE
)
```

# Research Narrative

My career focuses on making environmental data more useful to diverse communities. I use ethnographic and design methods to interrogate research practices and infrastructure, learn and iterate. Early work at Washington University's Center for Air Pollution Impact and Trend Analysis (CAPITA) repurposed air quality datasets for research on long-range smoke and dust transport, introducing me to the Earth Science Information Partners (ESIP), where I later served as Community Director and Executive Director. Across this work, one refrain held: "it's not a technical problem, it's a social problem." In 2021, I returned to graduate school in Information Science under Leysia Palen, to study the social side. My research domain shifted from air quality to biological field stations. Currently, my research investigates information work practices in place-based environmental science—how researchers, field stations, and local and Indigenous communities produce, share, and steward data—and translates those findings into infrastructure design. This work draws on FAIR, CARE, and TRUST principles to connect research outputs to place, and informs ongoing projects including Ethnocode, and the iPlaces platform.

# Education

```{r, results='asis'}
CV$entries_data %>% 
  filter(section == 'education') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# Professional Experience

```{r, results='asis'}
CV$entries_data %>% 
  filter(section == 'industry_positions') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`} - {`end`}"),
    with = title,
    where = loc,
    why = description_bullets
  )
```

# Publications

For all publications see my [Google Scholar Profile](https://scholar.google.com/citations?user=PfGu6vEAAAAJ&hl=en&oi=sra)

```{r}
CV$entries_data %>%
filter(section == 'academic_articles') %>%
detailed_entries(
with = title, 
why = description_bullets
)
```

# Awards & Honors

```{r, results='asis'}
CV$entries_data %>% 
  filter(section == 'award') %>% 
  detailed_entries(
    what = institution,
    when = glue::glue("{`start`}"),
    with = title,
    why = description_bullets
  )
```

# Volunteer/Service

```{r}
CV$entries_data %>%
filter(section == 'service') %>%
detailed_entries(
with = title,
why = description_bullets
)
```
